---
title: "\"Maschine Learning Introduction\" course laboratory work 2"
output: html_document
---
```{r echo=FALSE}
library(knitr)
library(kohonen) 
opts_chunk$set(
  #cache.path = "../../../target/cache/",
  message = FALSE, tidy = FALSE,
  #fig.path = "../../../target/figures/",
  #base.dir = "../../../target/",
  animation.fun = hook_r2swf
)
```

Following libraries will be used
```{r}
source('./my_kohonen_som.R')
```
Set random seed for reproducible experiments.
```{r}
set.seed(1)
```

# Kohonen Neural Network use to solve clusterization problem

For neural network learning will be used Iris data set. This is perhaps the best known database to be found in the pattern recognition literature. The data set contains 3 classes of 50 instances each, where each class refers to a type of iris plant. One class is linearly separable from the other 2; the latter are NOT linearly separable from each other. 

Source: https://archive.ics.uci.edu/ml/datasets/Iris
```{r}
data(iris)
```

## Basic Kohonen network implementation learning
```{r}
data <- iris[,1:4]
network <- my_kohonen_som(data[sample(nrow(data)),], learnRate=0.5);
```

```{r}
predictionResult <- my_kohonen_som.predict(network, scale(data))
```

### Prediction result (total determined clusters count is **`r length(unique(predictionResult))`**)

```{r kable, echo=FALSE}
predictTable <- table(predictionResult, iris[,5])
kable(predictTable)
```

### Self--organizing map (SOM) network learning
```{r}
train.obs <- sample(nrow(iris), 50) # get the training set observations
train.set <- scale(iris[train.obs,][,-5]) # check info about scaling data below
test.set  <- scale(iris[-train.obs, ][-5],
                   center = attr(train.set, "scaled:center"),
                   scale  = attr(train.set, "scaled:scale"))
som.iris <- som(train.set, grid = somgrid(5, 5, "hexagonal"))
```

```{r}
plot(som.iris)
```

```{r}
som.prediction <- 
  predict(som.iris, newdata = test.set,
          trainX = train.set,
          trainY = classvec2classmat(iris[,5][train.obs]))
```

### Prediction result (total determined clusters count is **`r ncol(som.prediction)`**)
```{r kable1, echo=FALSE}
kable(table(iris[,5][-train.obs], som.prediction$prediction))
```

